What We Eval in the Shadows

### 2021-04-16 paper/main.tex
JS and environment of eval

\paragraph{Discussion} The variety of uses of \eval is evidenced by the number
of different forms observed in CRAN. In comparison, JavaScript \eval usage was more straightforward and more predictable as reported by \citet{oopsla12b}, with 98.6\% of the sites with only one form. Nevertheless, simple forms dominate in R also, and there are many cases where \eval could be replaced by less powerful constructs.

@@

The environment in which evaluation happens determines what is visible to the
computation started by \eval and the potential reach of its side-effects. The
second argument to \eval specifies that environment. Environments of \eval can be
classified into the following four kinds:

>>>>

\paragraph{Discussion} The variety of uses of \eval is evidenced by the number
of different forms observed in CRAN. In comparison, JavaScript \eval usage was more straightforward and more predictable as reported by \citet{oopsla12b}, with 98.7\% of the sites with only one form. Nevertheless, simple forms dominate in R also, and there are many cases where \eval could be replaced by less powerful constructs.

@@

Contrary to the Javasscript \eval, which does not precise the scope in which to evaluate,the second argument of \eval in R, \c{envir}, specifically is dedicated ot that. 
The environment in which evaluation happens determines what is visible to the
computation started by \eval and the potential reach of its side-effects. The
second argument to \eval specifies that environment. Environments of \eval can be
classified into the following four kinds:
